### 2014-02-26 src/paper.Rnw
update

>>>>

% On Mutation and Dataflow : W.E Eong
Wong et al~\cite{wong1994on} suggests random sampling of mutants from the complete population.

Wong and Mathur suggests constrained mutation~\cite{} which chooses specific mutation operators only.

% Empirical Evaluation of the Statement Deletion Mutation Operator : Offutt
Deng et al~\cite{deng2013empirical} considers the effect of using a single mutation operator -- the statement deletion operator. They define deletion for different language elements,
